\documentclass[twocolumn]{article}
% {amsart}
\usepackage[top=0.75in, left=0.65in, right=0.65in, bottom=0.6in]{geometry}

\usepackage{float}

% \usepackage{url}
% \usepackage{xurl}
\usepackage[pdftex]{hyperref}


% \usepackage{code}
% \usepackage{cite}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
% IPA symbols. safe turns off overrides for like \! which I still want
\usepackage[safe]{tipa}
\usepackage{chessboard}
\usepackage{supertabular}

\usepackage[most]{tcolorbox}

% lets me explicitly set a. or 1. etc. as enum label
% \usepackage{enumitem}

\pagestyle{empty}

\usepackage{ulem}
% go back to italics for emphasis, though
\normalem

\usepackage{natbib}

\interfootnotelinepenalty=0
\setlength{\footnotesep}{2em}

\newcommand\sfrac[2]{\!{}\,^{#1}\!/{}\!_{#2}}

% XXX the collection of crap above causes a first page
% with just "1" on it (probably conflicting packages). This
% magic just drops the first page, which is of course not
% the right solution, but...
\usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
\AtBeginDocument{\AtBeginShipoutNext{\AtBeginShipoutDiscard}}

\begin{document}

\title{Harder Drive: Hard drives we didn't want or need}
\author{Dr.~Tom~Murphy~VII~Ph.D.}\thanks{
Copyright \copyright\ 2022 the Regents of the Wikiplia Foundation.
Appears in SIGBOVIK~2022 with the
Input/Output error of the Association for Computational Heresy; {\em IEEEEEE!}
press, Verlag-Verlag volume no.~0x40-2A. 6.6e-11 $N m^2kg^{-2}$
}

\renewcommand\th{\ensuremath{{}^{\textrm{th}}}}
\newcommand\st{\ensuremath{{}^{\textrm{st}}}}
\newcommand\rd{\ensuremath{{}^{\textrm{rd}}}}
\newcommand\nd{\ensuremath{{}^{\textrm{nd}}}}

\renewcommand\paragraph[1]{\smallskip \noindent{\bf #1}\enspace}

\date{7 April 2022}

\maketitle \thispagestyle{empty}

\sloppypar


\section{Introduction}

\section{Conclusion}

\paragraph{Acknowledgements.}

I used {\tt nbdkit} to create block devices, which was a much sounder
idea than writing my own kernel drivers. The code for sending and
receiving pings was adapted from {\tt liboping}.

Thanks to Rose, William, Sophia, Reed, Jessica, Max, and Finn for
donating their nasal swabs to the project. I especially appreciate
that they gave me these samples without any information about what I
was even doing with them. That's true friendship. By the way, human
cloning is possible now. Just sayin'.

If you have a computer connected to the internet, then I attempted
to send it a message during the course of this project. If your
computer responded, then thank you for configuring it that way.

Finally I would like to thank the SIGBOVIK program committee for letting
me store this file in the proceedings:

%
% tar  -c -M  --record-size=2560 --tape-length=2953c --new-volume-script='echo out${TAR_VOLUME}.tar >& ${TAR_FD}' --file=out1.tar QR_code.bz2

% (qr-encoded?

\nocite{murphy2019eloworld}

\bibliography{pingu}{}
\bibliographystyle{plain}

\end{document}

